SIMD\slash SIMT-vectorized Thermo-chemical Source Term Evaluation

### 2018-02-09 paper.tex
update

\begin{table}[htb]
\centering
\begin{tabular}{@{}l l l l l@{}}
\toprule
Model & Instruction Set & Vector Width & Cores & Identifier \\
\midrule
Intel Xeon X5650 & SSE4.2 & \SI{128}{\bit} & $2 \times 6$ & \texttt{sse} \\
Intel E5-2690 V3 & AVX2 & \SI{256}{\bit} & $2 \times 12$ & \texttt{haswell} \\
\bottomrule
\end{tabular}
\label{t:cpus}
\caption{The CPU configurations used in this study.}
\end{table}
\begin{table}
\centering
\begin{tabular}{@{}l l l l l@{}}
\toprule
Model & CUDA Version & CUDA Cores & Identifier \\
\midrule
Tesla C2075 & 9.0.176 & \num{448} & \texttt{C2075} \\
Tesla K40m & 8.0.61 & 2880 & \texttt{K40m} \\
\bottomrule
\end{tabular}
\label{t:gpus}
\caption{The GPU configurations used in this study.}
\end{table}

>>>>

\begin{table}[htb]
\centering
\begin{tabular}{@{}l l l l l@{}}
\toprule
Model & Instruction Set & Vector Width & Cores & Identifier \\
\midrule
Intel Xeon X5650 & SSE4.2 & \SI{128}{\bit} & $2 \times 6$ & \texttt{sse4.2} \\
Intel E5-2690 V3 & AVX2 & \SI{256}{\bit} & $2 \times 12$ & \texttt{avx2} \\
\bottomrule
\end{tabular}
\label{t:cpus}
\caption{The CPU configurations used in this study.}
\end{table}
\begin{table}
\centering
\begin{tabular}{@{}l l l l l@{}}
\toprule
Model & CUDA Version & CUDA Cores & Identifier \\
\midrule
Tesla C2075 & 9.0.176 & \num{448} & \texttt{C2075} \\
Tesla K40m & 8.0.61 & 2880 & \texttt{K40m} \\
\bottomrule
\end{tabular}
\label{t:gpus}
\caption{The GPU configurations used in this study.}
\end{table}
